%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Modified for Premium Two-Page Layout by ChatGPT (2025)
%------------------------

\documentclass[letterpaper,11pt]{article}

% Use Geometry for better margin control
\usepackage[margin=0.35in]{geometry}
\usepackage[default]{sourcesanspro}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{titlesec}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeHeading}[4]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} \emph{#2}  \\
    \textbf{{\small #3}} & {\small #4} \\
  \end{tabular*}
  \vspace{-10pt} % Tighter spacing after the single line
}
% (Ignores argument #2 "Context" entirely to save space)
\newcommand{\resumeProjectHeading}[3]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & {\small #3} \\
    \vspace{-24pt}
  \end{tabular*}
  \vspace{-10pt}
}
% Layout: University | Degree (Left) --- Date (Right)
\newcommand{\resumeEducationHeading}[3]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} $|$ \emph{#2} & {\small #3} \\
  \end{tabular*}
  \vspace{-14pt}
}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
% "label=\tiny$\bullet$" forces a small, sharp dot instead of a dash
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, labelsep=4pt, itemsep=0pt, label=\tiny$\bullet$]}
% Increased itemsep slightly for breathing room
\newcommand{\resumeItemListEnd}{\end{itemize}}

% ... resume starts here ...

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{ \huge Suraj Bijjala} \\ \vspace{2pt}
    \small
    +1 (240) 991-2736 $|$
    \href{mailto:suraj.bijjala.2@gmail.com}{{suraj.bijjala.2@gmail.com}} $|$
    \href{https://www.linkedin.com/in/surajbijjala}{{linkedin.com/in/surajbijjala}} $|$
    \href{https://www.datascienceportfol.io/surajbijjala}{Portfolio} $|$ \href{https://github.com/surajbijjala1}{{github.com/surajbijjala1}}
\end{center}

\vspace{-18pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{
 \textbf{AI Engineer} with over 2 year of experience designing and deploying end-to-end artificial intelligence solutions, \textbf{RAG architectures}, and scalable data pipelines. Specialized in leveraging \textbf{Large Language Models (LLMs)}, Python, and vector databases to build autonomous agents and generative AI applications. Combines a strong foundation in enterprise \textbf{Data Engineering} and backend development to bridge the gap between experimental AI models and production-ready business systems.
}
\vspace{-8pt}

%-----------SKILLS-----------
\section{Technical Skills}
\small{
\linespread{1.15}\selectfont
 \textbf{AI \& ML}{: LLMs (OpenAI, Claude, Gemini), RAG Architecture, Model Fine-Tuning, Vector Databases (FAISS), Supervised \& Reinforcement Learning, Multi-Agent Systems, Tool Calling, AI Guardrails \& Safety, Prompt Engineering, Chroma, Pinecone, NLP, Zapier, n8n} \\
 \textbf{Languages \& Frameworks}{: Python (Pandas, PyTorch, FastAPI), Node.js, TypeScript, JavaScript, SQL, React, Angular, NestJS, REST API} \\
 \textbf{Data Engineering \& Cloud}{: Snowflake, PostgreSQL, dbt Cloud, Apache Airflow, AWS (S3, Lambda, RDS), Azure} \\
 \textbf{DevOps \& Architecture}{: Docker, CI/CD, Git, GitHub Actions, Nx Monorepo, System Design, JWT, RBAC}
}
\vspace{-8pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
    {My Inner Archive - AI-Powered RAG Journal}{}{Apr 2026}\vspace{-3pt}
    \resumeItemListStart
      \resumeItem{Architected a secure, full-stack \textbf{Retrieval-Augmented Generation (RAG)} platform that acts as a localized AI companion, exclusively utilizing a user's historical journal entries to synthesize personalized reflections and insights.}
      \resumeItem{Engineered a resilient inference backend with smart fallback routing, seamlessly integrating the \textbf{Gemini API} for cloud-based generation while supporting fully private, local model execution via \textbf{Ollama}.}
      \resumeItem{Developed complex frontend data visualizations from scratch utilizing raw SVGs and React state, mapping emotional patterns and user context stored securely in \textbf{Supabase (PostgreSQL)} with JWT authentication.}
      \resumeItem{\textbf{Tech Stack:} React.js, Node.js, Express.js, Supabase (PostgreSQL), Gemini API, Ollama, RAG, JWT, Anti Gravity, Claude Code}
    \resumeItemListEnd
\vspace{-14pt}

  \resumeProjectHeading
    {AI Platform - Conversational RAG Engine}{}{Sep 2025}
    \resumeItemListStart
      \resumeItem{Architected a \textbf{Retrieval-Augmented Generation (RAG)} pipeline using Python and \textbf{LangChain}, enabling the system to reason over and synthesize unstructured technical knowledge.}
      \resumeItem{Optimized vector indexing strategies using \textbf{FAISS} to manage 10,000+ document chunks, achieving sub-second retrieval latency and implementing robust \textbf{validation loops} for queries.}
      \resumeItem{Designed modular backend parsing pipelines that reduced ingestion time by 40\%, seamlessly integrating public \textbf{LLMs} with strict \textbf{AI guardrails} to deliver safe, accurate responses.}
      \resumeItem{\textbf{Tech Stack:} Python, LangChain, RAG Architecture, FAISS, LLMs, Backend APIs.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeHeading{Onki AI}{}{ -- AI Engineer}{Sep 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Architected an automated ETL pipeline using \textbf{Azure OpenAI} to extract and structure raw HTML into validated JSON schemas, enriching data for over 3,500 retail products.}
    \resumeItem{Implemented \textbf{RAG systems} connected to internal data sources, utilizing vector embeddings and \textbf{tool calling} to power a conversational Voice AI agent with a reliable source of truth.}
    \resumeItem{Deployed secure \textbf{PostgreSQL} databases on Azure via Docker, implementing strict \textbf{RBAC} for multi-tenant isolation and automating \textbf{Data Quality} workflows via Prefect.}
    \resumeItem{\textbf{Tech Stack:} Python, Azure OpenAI, PostgreSQL, Docker, Prefect, RAG, ETL Pipelines.}
  \resumeItemListEnd
\vspace{-4pt}

\resumeHeading{LTIMindtree (Client: Colgate-Palmolive)}{}{ -- Data Engineer}{Jul 2021 -- Dec 2023}
  \resumeItemListStart
    \resumeItem{Architected a scalable \textbf{3-layer data backend} (Stage, Curated, Consumption) in \textbf{Snowflake}, securely migrating 10TB of enterprise records from legacy SAP S4/ECC via \textbf{HVR replication}.}
    \resumeItem{Engineered robust data transformation pipelines using \textbf{dbt Cloud} and \textbf{Apache Airflow}, computing complex multi-granular aggregations to support high-performance analytical models.}
    \resumeItem{Developed interactive global analytics dashboards in \textbf{Sigma Computing}, automating cross-timezone data refreshes to deliver real-time operational visibility to executive stakeholders.}
    \resumeItem{\textbf{Tech Stack:} Snowflake, dbt Cloud, Apache Airflow, Python, SQL, SAP S4/ECC, Sigma Computing.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeEducationHeading
    {University of Maryland, College Park}{M.Eng. in Software Engineering $|$ GPA: 3.8}{Jan 2024 -- Dec 2025}
  \resumeEducationHeading
    {VNR Vignana Jyothi Institute of Engineering}{B.Tech. in Computer Science $|$ GPA: 3.5}{Aug 2017 -- Jul 2021}
\resumeSubHeadingListEnd
\vspace{-12pt}

% %-----------CERTIFICATIONS-----------
% \section{Certifications}
% \resumeSubHeadingListStart
%   \resumeItem{\textbf{Machine Learning} -- Stanford University }
%   \vspace{-4pt}
%   \resumeItem{\textbf{Python for Data Science and AI} -- IBM }
% \resumeSubHeadingListEnd

\end{document}
