%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Modified for Premium Two-Page Layout by ChatGPT (2025)
%------------------------

\documentclass[letterpaper,11pt]{article}

% Use Geometry for better margin control
\usepackage[margin=0.35in]{geometry}
\usepackage[default]{sourcesanspro}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{titlesec}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeHeading}[4]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} \emph{#2}  \\
    \textbf{{\small #3}} & {\small #4} \\
  \end{tabular*}
  \vspace{-10pt} % Tighter spacing after the single line
}
% (Ignores argument #2 "Context" entirely to save space)
\newcommand{\resumeProjectHeading}[3]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & {\small #3} \\
    \vspace{-24pt}
  \end{tabular*}
  \vspace{-10pt}
}
% Layout: University | Degree (Left) --- Date (Right)
\newcommand{\resumeEducationHeading}[3]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} $|$ \emph{#2} & {\small #3} \\
  \end{tabular*}
  \vspace{-14pt}
}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
% "label=\tiny$\bullet$" forces a small, sharp dot instead of a dash
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, labelsep=4pt, itemsep=0pt, label=\tiny$\bullet$]}
% Increased itemsep slightly for breathing room
\newcommand{\resumeItemListEnd}{\end{itemize}}

% ... resume starts here ...

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{ \huge Suraj Bijjala} \\ \vspace{2pt}
    \small
    +1 (240) 991-2736 $|$
    \href{mailto:suraj.bijjala.2@gmail.com}{{suraj.bijjala.2@gmail.com}} $|$
    \href{https://www.linkedin.com/in/surajbijjala}{{linkedin.com/in/surajbijjala}} $|$
    \href{https://www.datascienceportfol.io/surajbijjala}{Portfolio} $|$ \href{https://github.com/surajbijjala1}{{github.com/surajbijjala1}}
\end{center}

\vspace{-14pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{
 \textbf{AI Data Engineer} with over 2 years of experience in the design of scalable ETL pipelines and high-performance \textbf{RAG systems}. Specialized in modernizing cloud infrastructure on \textbf{AWS} and \textbf{Snowflake}, consistently delivering over 70\% optimization in query performance. Dedicated to bridging the gap between traditional data modeling and \textbf{Generative AI}, using \textbf{Python}, \textbf{SQL}, and Vector Databases to deploy production-ready solutions.
}
\vspace{-8pt}

%-----------SKILLS-----------
\section{Technical Skills}
\small{
\linespread{1.15}\selectfont
 \textbf{Languages \& Frameworks}{: Python, PySpark, SQL, Java, JavaScript, TypeScript, Node.js, Angular, React, Bash, PyTorch, Pandas, Numpy} \\
 \textbf{Data Engineering}{: dbt Cloud, Snowflake, PostgreSQL, MongoDB, VectorDB, Tableau, Power BI, Sigma Computing, Apache Airflow, HVR Replication, ETL/ELT, SAP S4/ECC} \\
 \textbf{Cloud \& DevOps}{: AWS (EC2, S3, RDS, Lambda), Azure, Docker, Git, GitHub Actions, Jira} \\
 \textbf{AI \& Machine Learning}{: Generative AI (RAG, LangChain), Large Language Models (LLMs), Model Fine-Tuning, Vector Databases (FAISS, ChromaDB), Supervised \& Reinforcement Learning, Multi-Agent Systems, Tool Calling, AI Guardrails \& Safety, Prompt Engineering}}
\vspace{-8pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeHeading{Onki AI}{}{ -- AI Data Engineer}{Sep 2025 -- Present}\vspace{-3pt}
  \resumeItemListStart
    \resumeItem{Architected a scalable \textbf{ETL pipeline} on Azure, utilizing \textbf{OpenAI APIs} and NLP to scrape, extract, and structure data from raw HTML, enriching JSONs for 3,500+ retail products.}
    \resumeItem{Engineered a resilient \textbf{Data Governance} framework by unifying fragmented inventory lists into a centralized \textbf{PostgreSQL} catalog, serving as a reliable \textbf{source of truth} for Voice AI workflows.}
    \resumeItem{Implemented robust data quality management using modular \textbf{Python} scripts and automated orchestration, leveraging \textbf{Role-Based Access Control} to guarantee secure multi-tenant data isolation.}
    \resumeItem{\textbf{Tech Stack:} Python, Azure OpenAI, PostgreSQL, Docker, Prefect, Generative AI.}
  \resumeItemListEnd
\vspace{-4pt}

  \resumeHeading{LTIMindtree (Client: Colgate-Palmolive)}{}{ -- Senior Data Engineer}{Nov 2022 -- Dec 2023}\vspace{-3pt}
  \resumeItemListStart
    \resumeItem{Designed and deployed a \textbf{3-layer data architecture} (Stage, Curated, Consumption) in \textbf{Snowflake}, enabling scalable analytical models and ensuring high-performance global reporting capabilities.}
    \resumeItem{Engineered automated \textbf{ELT transformations} within \textbf{dbt Cloud} to build denormalized master data tables, orchestrating complex workflows via \textbf{Apache Airflow} to ensure 98\% data accuracy.}
    \resumeItem{Developed and optimized global analytics dashboards in \textbf{Sigma Computing} and replicated the same in \textbf{Tableau} and \textbf{Power BI}, configuring automated data pipelines to refresh \textbf{enterprise reports} 4-5 times daily across multiple international timezones.}
    \resumeItem{\textbf{Tech Stack:} Snowflake, dbt Cloud, Apache Airflow, Sigma Computing, SQL, Data Modeling.}
  \resumeItemListEnd
\vspace{-4pt}

  \resumeHeading{LTIMindtree (Client: Colgate-Palmolive)}{}{ -- Junior Data Engineer}{Jul 2021 -- Oct 2022}\vspace{-3pt}
  \resumeItemListStart
    \resumeItem{Facilitated the secure migration of \textbf{10TB of enterprise data} from legacy \textbf{SAP S4} and ECC systems to Snowflake, utilizing \textbf{HVR replication} to establish a modernized data infrastructure.}
    \resumeItem{Translated legacy SAP extraction logic into scalable \textbf{Stage layer models}, computing complex multi-granular aggregations in the curated layer to optimize \textbf{Snowflake virtual warehouses}.}
    \resumeItem{Partnered with business stakeholders to transition legacy reports, building \textbf{interactive dashboards} that visualized critical inventory and customer service metrics to maintain business continuity and provide business insights.}
    \resumeItem{\textbf{Tech Stack:} Snowflake, SAP S4/ECC, HVR Replication, SAP BI, SQL, ELT/ETL.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {AI Interview Prep Platform - RAG System}{}{Sep 2025}\vspace{-3pt}
    \resumeItemListStart
      \resumeItem{Architected a \textbf{Retrieval-Augmented Generation (RAG)} engine using Python and LangChain, achieving sub-second retrieval latency for context-aware queries against a technical knowledge base.}
      \resumeItem{Optimized vector indexing strategies using \textbf{FAISS} to process and manage 10,000+ document chunks, maintaining high semantic relevance scores for \textbf{AI-driven content generation}.}
      \resumeItem{Designed modular \textbf{data parsing pipelines} that reduced document ingestion time by 40\%, ensuring the backend system could scale horizontally to handle diverse and complex file formats.}
      \resumeItem{\textbf{Tech Stack:} Python, LangChain, FAISS, Vector Search, NLP.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeEducationHeading
    {University of Maryland, College Park}{M.Eng. in Software Engineering $|$ GPA: 3.8}{Jan 2024 -- Dec 2025}
  \resumeEducationHeading
    {VNR Vignana Jyothi Institute of Engineering}{B.Tech. in Computer Science $|$ GPA: 3.5}{Aug 2017 -- Jul 2021}
\resumeSubHeadingListEnd
\vspace{-12pt}

% %-----------CERTIFICATIONS-----------
% \section{Certifications}
% \resumeSubHeadingListStart
%   \resumeItem{\textbf{Machine Learning} -- Stanford University }
%   \vspace{-4pt}
%   \resumeItem{\textbf{Python for Data Science and AI} -- IBM }
% \resumeSubHeadingListEnd

\end{document}
