%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Modified for Premium Two-Page Layout by ChatGPT (2025)
%------------------------

\documentclass[letterpaper,11pt]{article}

% Use Geometry for better margin control
\usepackage[margin=0.35in]{geometry}
\usepackage[default]{sourcesanspro}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{titlesec}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1}}
\newcommand{\resumeHeading}[4]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} \emph{#2}  \\
    \textbf{{\small #3}} & {\small #4} \\
  \end{tabular*}
  \vspace{-10pt} % Tighter spacing after the single line
}
% (Ignores argument #2 "Context" entirely to save space)
\newcommand{\resumeProjectHeading}[3]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & {\small #3} \\
    \vspace{-24pt}
  \end{tabular*}
  \vspace{-10pt}
}
% Layout: University | Degree (Left) --- Date (Right)
\newcommand{\resumeEducationHeading}[3]{
  \item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} $|$ \emph{#2} & {\small #3} \\
  \end{tabular*}
  \vspace{-14pt}
}


\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
% "label=\tiny$\bullet$" forces a small, sharp dot instead of a dash
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in, labelsep=4pt, itemsep=0pt, label=\tiny$\bullet$]}
% Increased itemsep slightly for breathing room
\newcommand{\resumeItemListEnd}{\end{itemize}}

% ... resume starts here ...

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{ \huge Suraj Bijjala} \\ \vspace{2pt}
    \small
    +1 (240) 991-2736 $|$
    \href{mailto:suraj.bijjala.2@gmail.com}{{suraj.bijjala.2@gmail.com}} $|$
    \href{https://www.linkedin.com/in/surajbijjala}{{linkedin.com/in/surajbijjala}} $|$
    \href{https://www.datascienceportfol.io/surajbijjala}{Portfolio} $|$ \href{https://github.com/surajbijjala1}{{github.com/surajbijjala1}}
\end{center}

\vspace{-16pt}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{
 \textbf{Software \& AI Engineer} with over 2 years of experience in backend development, scalable data pipelines, and system architecture. Proficient in \textbf{Python}, \textbf{Node.js}, and \textbf{SQL}, with a proven track record of migrating enterprise data and building robust APIs. Highly interested in applying artificial intelligence, leveraging \textbf{Large Language Models (LLMs)}, and building \textbf{RAG architectures} to bridge the gap between traditional software engineering and modern AI-driven solutions.
}
\vspace{-8pt}

%-----------SKILLS-----------
\section{Technical Skills}
\small{
\linespread{1.15}\selectfont
 \textbf{Languages \& Frameworks}{: Python (FastAPI, Pandas), Node.js, TypeScript, SQL, Angular, NestJS, React, Flask} \\
 \textbf{Cloud \& Architecture}{: AWS (S3, Lambda, RDS), Azure, Docker, CI/CD, Nx Monorepo, System Design, JWT, RBAC} \\
 \textbf{AI \& Machine Learning}{: LLMs (OpenAI, Claude), RAG Architecture, Vector Databases (FAISS, ChromaDB), Model Fine-Tuning, Multi-Agent Systems, AI Guardrails} \\
 \textbf{Databases \& Data Engineering}{: PostgreSQL, Snowflake, dbt Cloud, Apache Airflow, ETL/ELT, SAP S4/ECC}
}
\vspace{-8pt}

%-----------PROJECTS-----------
% PROJECT SELECTION RULE (Software Engineer roles):
% Pick 2 of the 3 fullstack projects based on best tech stack match for the JD:
%   - My Inner Archive (React, Node, Supabase/PostgreSQL, RAG, Gemini, Ollama, JWT)
%   - AI-Assisted Enterprise Task Management (NestJS, Angular, TypeScript, Nx, RBAC, JWT)
%   - GREBoost (add content when available)
% Default (no clear signal): use My Inner Archive + Task Management (shown below)
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
    {My Inner Archive - AI-Powered RAG Journal}{}{Apr 2026}\vspace{-3pt}
    \resumeItemListStart
      \resumeItem{Architected a secure, full-stack \textbf{Retrieval-Augmented Generation (RAG)} platform that acts as a localized AI companion, exclusively utilizing a user's historical journal entries to synthesize personalized reflections and insights.}
      \resumeItem{Engineered a resilient inference backend with smart fallback routing, seamlessly integrating the \textbf{Gemini API} for cloud-based generation while supporting fully private, local model execution via \textbf{Ollama}.}
      \resumeItem{Developed complex frontend data visualizations from scratch utilizing raw SVGs and React state, mapping emotional patterns and user context stored securely in \textbf{Supabase (PostgreSQL)} with JWT authentication.}
      \resumeItem{\textbf{Tech Stack:} React.js, Node.js, Express.js, Supabase (PostgreSQL), Gemini API, Ollama, RAG, JWT, Claude Code}
    \resumeItemListEnd
\vspace{-12pt}

  \resumeProjectHeading
    {AI-Assisted Enterprise Task Management System}{}{Feb 2026}
    \resumeItemListStart
      \resumeItem{Accelerated full-stack development by leveraging \textbf{AI Copilots} (Claude, Gemini) to architect a scalable \textbf{Nx monorepo} and deploy production-ready features rapidly.}
      \resumeItem{Engineered a \textbf{NestJS} API and Angular frontend with a custom \textbf{Role-Based Access Control} engine, hardening backend security via non-mocked \textbf{JWT authentication} across all endpoints.}
      \resumeItem{Developed a responsive Kanban dashboard using \textbf{TailwindCSS} and \textbf{RxJS} for dynamic client-side filtering, establishing a single source of truth for DTOs to eliminate code drift.}
      \resumeItem{\textbf{Tech Stack:} NestJS, Angular, TypeScript, Nx Monorepo, TailwindCSS, RxJS, JWT, AI Copilots.}
    \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeHeading{Onki AI}{}{ -- AI Software Engineer}{Sep 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Engineered the core backend by integrating an automated ETL pipeline with \textbf{Azure OpenAI}, parsing unstructured HTML into validated JSON schemas to drive data for 3,500+ products.}
    \resumeItem{Developed an end-to-end AI solution by connecting backend \textbf{RAG systems} to a frontend conversational \textbf{Voice AI agent}, utilizing vector embeddings and \textbf{tool calling} for real-time interactions.}
    \resumeItem{Architected scalable backend infrastructure via Docker and \textbf{PostgreSQL} on Azure, enforcing strict \textbf{RBAC} for multi-tenant isolation and automating modular workflows via \textbf{Prefect}.}
    \resumeItem{\textbf{Tech Stack:} Python, Azure OpenAI, PostgreSQL, Docker, Prefect, RAG, Backend Architecture.}
  \resumeItemListEnd
\vspace{-4pt}

  \resumeHeading{LTIMindtree (Client: Colgate-Palmolive)}{}{ -- Data Engineer}{Jul 2021 -- Dec 2023}
  \resumeItemListStart
    \resumeItem{Architected a scalable \textbf{3-layer data backend} (Stage, Curated, Consumption) in \textbf{Snowflake}, securely migrating 10TB of enterprise records from legacy \textbf{SAP S4/ECC} via HVR replication.}
    \resumeItem{Engineered robust backend data transformation pipelines using \textbf{dbt Cloud} and \textbf{Apache Airflow}, optimizing complex SQL aggregations to support high-performance analytical models.}
    \resumeItem{Designed automated reporting systems and global dashboards in \textbf{Sigma Computing}, translating complex backend analytics into actionable operational visibility for executive stakeholders.}
    \resumeItem{\textbf{Tech Stack:} Snowflake, dbt Cloud, Apache Airflow, Python, SQL, SAP S4/ECC, Sigma Computing.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-16pt}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeEducationHeading
    {University of Maryland, College Park}{M.Eng. in Software Engineering $|$ GPA: 3.8}{Jan 2024 -- Dec 2025}
  \resumeEducationHeading
    {VNR Vignana Jyothi Institute of Engineering}{B.Tech. in Computer Science $|$ GPA: 3.5}{Aug 2017 -- Jul 2021}
\resumeSubHeadingListEnd
\vspace{-12pt}

% %-----------CERTIFICATIONS-----------
% \section{Certifications}
% \resumeSubHeadingListStart
%   \resumeItem{\textbf{Machine Learning} -- Stanford University }
%   \vspace{-4pt}
%   \resumeItem{\textbf{Python for Data Science and AI} -- IBM }
% \resumeSubHeadingListEnd

\end{document}
